Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Multi-Notch Searches

### 2017-10-27 paper.tex
exampleOfWrongId

A specific example of a misassigned PSM is the example where the correct identification has oxidation and ammonia loss, but was identified as an unmodified peptide with score 10.
It is Frac9 scan 21230.
With G-PTM-D added modifications, it is clear that the correct identification has a mass difference of 0 and a score 20.

>>>>

A specific example of a misassigned PSM is the example where the correct identification has oxidation and ammonia loss, but was identified as an unmodified peptide with score 9.039 and mass difference of -1.03335 Da, with sequence QAFDDAIAELDTLNEDSYK, Jurkat Frac9 scan 20962.
With G-PTM-D added modifications, the correct peptide is identified with sequence [PeptideTermMod:Ammonia loss on Q]QAFDDAIAELDTLNEDSY[Mod:Oxidation on Y]K. It has a mass difference of -0.00171(-0.79458 ppm) and a score 19.222.
